---
title: "elMatch-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{elMatch-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#devtools::install_github('liza-wood/elMatch')
library(elMatch)
```

Identify the URLs where the survey results are kept and plug them in to the functions that pull out research interests and needs. 
```{r, warning = F, message = F}
student_url <- 'https://docs.google.com/spreadsheets/d/17Q0SXTqrhpND8rADn-3I4SZGLkcdta3HmFzD9ygO69s/edit?resourcekey#gid=454745221'
project_url <- 'https://docs.google.com/spreadsheets/d/1Gc6vWHrzsFedukHba85GVMlHWcl6NSrs5m9KcgXVx70/edit?resourcekey#gid=415684977'
p_mat <- pull_research_needs(project_url, student_url)
s_mat <- pull_student_interest(student_url)
```

Now we can compare the two matrices and identify the top student matches for each project. Note that you can select a cutoff score between 0-3, where 3 is a perfect match.
```{r}
proj_list <- identify_top_matches(p_mat, s_mat, cutoff = 1)
```

Then we can take a look at the top candidates per project. 
```{r}
proj_list[[2]]
```

We can also pull out a dictionary of all students and projects. 
```{r}
p_index <- get_project_index(project_url)
p_index
s_index <- get_student_index(student_url)
s_index
```


Note that the matching has NOT YET considered actual assessment. We can run this next function to send emails to each student for skills they marked as having experience in. This looks at the student index to send, and then it will update the index with a 'sent' message so that students are not repeatedly sent assessments (I hope). Or we could just make this into a Qualtrics survey with better conditionality. 

```{r, eval = F}
email_assessments(sender = 'belwood@ucdavis.edu')
```

TODO: 
* Function that grades assessments
* Match those scores back to students to provide an additional metric for matching
